geochemistry

### 2025-02-17 geochemistry.qmd
Macbook session upload

@@

@@

p_sp18 <- sp18_long |>
  mutate(Phase = factor(Phase, levels = c("Observed", "Quartz", "Dolomite", "Halite", "Background", "Difference"))) |>
  ggplot(aes(x = Angle, y = Count, colour = Phase)) +
  geom_line(linewidth = 0.5) +
  labs(x = "Diffraction Angle", y = "Intensity") +
  theme_minimal() +
  coord_cartesian(ylim = c(-5000, 50000)) +
  geom_point(data = sp18_marks, aes(x = Angle, y = Intensity + 600, colour = Phase), size = 3, shape = 18) +
  geom_label(data = sp18_marks, aes(x = Angle, y = Intensity, label = d), 
            size = 3, fill = "white", label.size = 0.2, vjust = -1, show.legend = FALSE) +
  scale_colour_manual(values = c("lightsteelblue3", "salmon", "steelblue1", "green" ,"orchid","snow4")) +
  annotate(geom = "table", x = 75, y = 50000, label = list(cbind(sp18_perc)))

@@

p_sp58 <- sp58_long |>
  mutate(Phase = factor(Phase, levels = c("Observed", "Quartz", "Calcite", "Background", "Difference"))) |>
  ggplot(aes(x = Angle, y = Count, colour = Phase)) +
  geom_line(linewidth = 0.5) +
  labs(x = "Diffraction Angle", y = "Intensity") +
  theme_minimal() +
  coord_cartesian(ylim = c(-5000, 50000)) +
  geom_point(data = sp58_marks, aes(x = Angle, y = Intensity + 600, colour = Phase), size = 3, shape = 18) +
  geom_label(data = sp58_marks, aes(x = Angle, y = Intensity, label = d), 
            size = 3, fill = "white", label.size = 0.2, vjust = -1, show.legend = FALSE) +
  scale_colour_manual(values = c("lightsteelblue3", "salmon", "steelblue1" ,"orchid","snow4")) +
  annotate(geom = "table", x = 75, y = 50000, label = list(cbind(sp58_perc)))

>>>>

# Colour codes
## Observed = "lightsteelblue3"
## Quartz = "salmon"
## Dolomite = "steelblue1"
## Calcite = "darkseagreen"
## Halite = "darkgoldenrod1"
## Background = "orchid"
## Difference = "snow4"

@@

# SP7 Cabo S. Vicente

sp7_marks <- xrd_marks |>
  filter(Sample == "SP7")
sp7_perc <- xrd_perc |>
  filter(Sample == "SP7") |>
  select(-Sample, -ESD)

sp7_xrd <- sp7_xrd |> 
  dplyr::mutate(Difference = Observed - Calculated - 3000) |> 
  rename(Quartz = `Quartz (SiO2)`) |> 
  rename(Dolomite = `Dolomite (CaMg(CO3)2)`)

sp7_long <- sp7_xrd %>%
  select(-Quartz_nb, -Dolomite_nb) |>
  pivot_longer(cols = c(Difference, Background, Observed, Quartz, Dolomite), 
               names_to = "Phase", 
               values_to = "Count")

p_sp7 <- sp7_long |>
  mutate(Phase = factor(Phase, levels = c("Observed", "Quartz", "Dolomite", "Background", "Difference"))) |>
  ggplot(aes(x = Angle, y = Count, colour = Phase)) +
  geom_line(linewidth = 0.5) +
  labs(x = "Diffraction Angle", y = "Intensity") +
  theme_minimal() +
  coord_cartesian(ylim = c(-5000, 65000)) +
  geom_point(data = sp7_marks, aes(x = Angle, y = Intensity + 600, colour = Phase), size = 3, shape = 18) +
  geom_label(data = sp7_marks, aes(x = Angle, y = Intensity, label = d), 
            size = 3, fill = "white", label.size = 0.2, vjust = -1, show.legend = FALSE) +
  scale_colour_manual(values = c("lightsteelblue3", "salmon", "steelblue1" ,"orchid","snow4")) +
  annotate(geom = "table", x = 75, y = 60000, label = list(cbind(sp7_perc)))

# SP10

sp10_marks <- xrd_marks |>
  filter(Sample == "SP10")
sp10_perc <- xrd_perc |>
  filter(Sample == "SP10") |>
  select(-Sample, -ESD)

sp10_xrd <- sp10_xrd |> 
  dplyr::mutate(Difference = Observed - Calculated - 3000)

sp10_long <- sp10_xrd %>%
  pivot_longer(cols = c(Difference, Background, Observed, Quartz, Calcite), 
               names_to = "Phase", 
               values_to = "Count")

p_sp10 <- sp10_long |>
  mutate(Phase = factor(Phase, levels = c("Observed", "Quartz", "Calcite", "Background", "Difference"))) |>
  ggplot(aes(x = Angle, y = Count, colour = Phase)) +
  geom_line(linewidth = 0.5) +
  labs(x = "Diffraction Angle", y = "Intensity") +
  theme_minimal() +
  coord_cartesian(ylim = c(-5000, 55000)) +
  geom_point(data = sp10_marks, aes(x = Angle, y = Intensity + 600, colour = Phase), size = 3, shape = 18) +
  geom_label(data = sp10_marks, aes(x = Angle, y = Intensity, label = d), 
            size = 3, fill = "white", label.size = 0.2, vjust = -1, show.legend = FALSE) +
  scale_colour_manual(values = c("lightsteelblue3", "salmon", "steelblue1" ,"orchid","snow4")) +
  annotate(geom = "table", x = 75, y = 55000, label = list(cbind(sp10_perc)))

# SP 14
sp14_marks <- xrd_marks |>
  filter(Sample == "SP14")
sp14_perc <- xrd_perc |>
  filter(Sample == "SP14") |>
  select(-Sample, -ESD)

sp14_xrd <- sp14_xrd |> 
  dplyr::mutate(Difference = Observed - Calculated - 3000)

sp14_long <- sp14_xrd %>%
  select(-Quartz_nb, -Dolomite_nb, -Halite_nb) |>
  pivot_longer(cols = c(Difference, Background, Observed, Quartz, Dolomite, Halite), 
               names_to = "Phase", 
               values_to = "Count")

p_sp14 <- sp14_long |>
  mutate(Phase = factor(Phase, levels = c("Observed", "Quartz", "Dolomite", "Halite", "Background", "Difference"))) |>
  ggplot(aes(x = Angle, y = Count, colour = Phase)) +
  geom_line(linewidth = 0.5) +
  labs(x = "Diffraction Angle", y = "Intensity") +
  theme_minimal() +
  coord_cartesian(ylim = c(-5000, 50000)) +
  geom_point(data = sp14_marks, aes(x = Angle, y = Intensity + 600, colour = Phase), size = 3, shape = 18) +
  geom_label(data = sp14_marks, aes(x = Angle, y = Intensity, label = d), 
            size = 3, fill = "white", label.size = 0.2, vjust = -1, show.legend = FALSE) +
  scale_colour_manual(values = c("lightsteelblue3", "salmon", "steelblue1", "darkgoldenrod1" ,"orchid","snow4")) +
  annotate(geom = "table", x = 75, y = 50000, label = list(cbind(sp14_perc)))

# SP15

sp15_marks <- xrd_marks |>
  filter(Sample == "SP15")
sp15_perc <- xrd_perc |>
  filter(Sample == "SP15") |>
  select(-Sample, -ESD)

sp15_xrd <- sp15_xrd |> 
  dplyr::mutate(Difference = Observed - Calculated - 3000)

sp15_long <- sp15_xrd %>%
  select(-Quartz_nb, -Dolomite_nb) |>
  pivot_longer(cols = c(Difference, Background, Observed, Quartz, Dolomite), 
               names_to = "Phase", 
               values_to = "Count")

p_sp15 <- sp15_long |>
  mutate(Phase = factor(Phase, levels = c("Observed", "Quartz", "Dolomite", "Background", "Difference"))) |>
  ggplot(aes(x = Angle, y = Count, colour = Phase)) +
  geom_line(linewidth = 0.5) +
  labs(x = "Diffraction Angle", y = "Intensity") +
  theme_minimal() +
  coord_cartesian(ylim = c(-5000, 55000)) +
  geom_point(data = sp15_marks, aes(x = Angle, y = Intensity + 600, colour = Phase), size = 3, shape = 18) +
  geom_label(data = sp15_marks, aes(x = Angle, y = Intensity, label = d), 
            size = 3, fill = "white", label.size = 0.2, vjust = -1, show.legend = FALSE) +
  scale_colour_manual(values = c("lightsteelblue3", "salmon", "steelblue1" ,"orchid","snow4")) +
  annotate(geom = "table", x = 75, y = 55000, label = list(cbind(sp15_perc)))

@@

p_sp18 <- sp18_long |>
  mutate(Phase = factor(Phase, levels = c("Observed", "Quartz", "Dolomite", "Halite", "Background", "Difference"))) |>
  ggplot(aes(x = Angle, y = Count, colour = Phase)) +
  geom_line(linewidth = 0.5) +
  labs(x = "Diffraction Angle", y = "Intensity") +
  theme_minimal() +
  coord_cartesian(ylim = c(-5000, 50000)) +
  geom_point(data = sp18_marks, aes(x = Angle, y = Intensity + 600, colour = Phase), size = 3, shape = 18) +
  geom_label(data = sp18_marks, aes(x = Angle, y = Intensity, label = d), 
            size = 3, fill = "white", label.size = 0.2, vjust = -1, show.legend = FALSE) +
  scale_colour_manual(values = c("lightsteelblue3", "salmon", "steelblue1", "palevioletred3" ,"orchid","snow4")) +
  annotate(geom = "table", x = 75, y = 50000, label = list(cbind(sp18_perc)))

@@

p_sp58 <- sp58_long |>
  mutate(Phase = factor(Phase, levels = c("Observed", "Quartz", "Calcite", "Background", "Difference"))) |>
  ggplot(aes(x = Angle, y = Count, colour = Phase)) +
  geom_line(linewidth = 0.5) +
  labs(x = "Diffraction Angle", y = "Intensity") +
  theme_minimal() +
  coord_cartesian(ylim = c(-5000, 50000)) +
  geom_point(data = sp58_marks, aes(x = Angle, y = Intensity + 600, colour = Phase), size = 3, shape = 18) +
  geom_label(data = sp58_marks, aes(x = Angle, y = Intensity, label = d), 
            size = 3, fill = "white", label.size = 0.2, vjust = -1, show.legend = FALSE) +
  scale_colour_manual(values = c("lightsteelblue3", "salmon", "darkseagreen" ,"orchid","snow4")) +
  annotate(geom = "table", x = 75, y = 50000, label = list(cbind(sp58_perc)))
